Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield

### 2017-12-04 Tex/Paper.tex
Reflow

% ******************************************************************************************************************** %
\begin{document}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section{Introduction}\label{S:I}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection{AWAKE Run 2}\label{S:I:AWAKE}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section[\label{S:M}]{Method}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection{Drive Beam Parameters}\label{S:M:Setup}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection{Witness Beam Parameters}\label{S:M:Setup}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection{Simulation parameters}\label{SIM}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section{Beam Loading}\label{S:BL}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section{Parameter Optimisation}\label{S:PO}
% ******************************************************************************************************************** %

@@

Figure~\ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An
initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the
charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charge ranges from $10\unit{pC}$ to
$300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from Fig.
\ref{Fig:BeamQ} (red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum
energy spread with an initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam
charges tend to underload the electric field, while higher beam charges tend to overload it. It is also clear that
longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the
wake, thus producing a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is
preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}). As the witness beam charge
increases, the fraction of slices with preserved emittance increases \textendash as expected from an earlier onset of
the bubble formation \textendash and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that
operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the
expense of an increase of relative energy spread by a factor of two.

@@

% ******************************************************************************************************************** %
\section{Conclusion}\label{S:C}
% ******************************************************************************************************************** %

@@

\section{Acknowledgements}\label{Ack}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\bibliography{Bibliography,Additional}
\end{document}
% ******************************************************************************************************************** %

>>>>

% ************************************************************************************************ %
\begin{document}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\section{Introduction}\label{S:I}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\subsection{AWAKE Run 2}\label{S:I:AWAKE}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\section[\label{S:M}]{Method}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\subsection{Drive Beam Parameters}\label{S:M:Setup}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\subsection{Witness Beam Parameters}\label{S:M:Setup}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\subsection{Simulation parameters}\label{SIM}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\section{Beam Loading}\label{S:BL}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\section{Parameter Optimisation}\label{S:PO}
% ************************************************************************************************ %

@@

Figure~\ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charge ranges from $10\unit{pC}$ to $300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from Fig.~\ref{Fig:BeamQ} (red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to underload the electric field, while higher beam charges tend to overload it. It is also clear that longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the wake, thus producing a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction of slices with preserved emittance increases \textendash as expected from an earlier onset of the bubble formation \textendash and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.

@@

% ************************************************************************************************ %
\section{Conclusion}\label{S:C}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\section{Acknowledgements}\label{Ack}
% ************************************************************************************************ %

@@

% ************************************************************************************************ %
\bibliography{Bibliography,Additional}
\end{document}
% ************************************************************************************************ %
